Appunti di Matematica

### 2021-10-14 Analisi Matematica/mat.tex
mat
miglioramento dei grafici

    \filldraw  (0,0.3) circle (2pt) node[align=left,   below] {1}
    (1,0.11) circle (2pt) node[align=left,   below] {2}
    (-1,-0.4) circle (2pt) node[align=left,   below] {0}
    (-1,0.1) circle (2pt) node[align=left,   below] {3}
    (0.1,-0.5) circle (2pt) node[align=left,   below] {4};
\end{tikzpicture}

>>>>

    \filldraw  (0,0.3) circle (2pt) node[align=left,   below] {1}
    (-0.52,0.3) node[align=left,   below] {B}
    (0.55,0.11) circle (2pt) node[align=left,   below] {2}
    (-1,-0.4) circle (2pt) node[align=left,   below] {0}
    (-1,0.1) circle (2pt) node[align=left,   below] {3}
    (0.6,-0.55) circle (2pt) node[align=left,   below] {4};
\end{tikzpicture}
